Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and interpolation-extrapolation capacity validation

### 2022-10-18 Article.tex
Remove Johnson-Cook 1985

For several years, many researchers have developed methods to predict the thermomechanical behavior of materials under hot working conditions using constitutive models. Thus, various forms of constitutive equations have been proposed to describe the flow of materials, among which, phenomenological, semi-empirical, physical models or models based on Artificial Neural Networks (ANN) \cite{Lin-2011, Shin-2010, Rusinek-2010, Pantale-2021}. Among the large number of models available in the literature, the Johnson-Cook (JC) \cite{Johnson-1983, Johnson-1985} and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in finite element codes. The Johnson-Cook model is the most widely used because it is simple to identify and use and has few parameters to determine \cite{Khan-2004, NematNasser-2003}. However, this model, in its original state, has some shortcomings related to nonlinear coupling phenomena not taken into account in the material behavior. We refer here to strain hardening, strain rate hardening and thermal effects that are taken into account in a non-coupled manner in the JC model as analyzed by Jia \eal \cite{Jia-2021}. To circumvent these shortcomings, several modified forms of the Johnson-Cook model have been developed in the past \cite{Rule-1998, Vural-2003, Lin-2010, Lin-2012, Li-2013, Zhou-2019, Zhang-2015}. Due to its more physics-based formulation, the ZA model is often preferred to the JC model because it allows the coupling of strain rate and temperature effects \cite{Johnson-1988, Voyiadjis-2005, Dey-2007}. However, this model has other drawbacks related to the limit value of the test temperature. Indeed, this model applies only to low strain rates and for temperatures limited to about 60~\% of $T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005, Lee-2005, Chen-2007, Lee-2006}. Moreover, this model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009}. In order to reduce these shortcomings (and to apply this model to a wider range of temperatures) of the ZA model, modified forms of Zerilli-Armstrong (MZA) have been proposed by several authors in recent years \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}.

@@

The JC model as mentioned above, is one of the most widely used analytical models as it can be applied to several materials under different conditions of strain, strain rate and temperature. However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate and temperature. Indeed, it is formulated by describing the effect of each physical parameter (strain, strain rate and temperature) separately as a factor in the mathematical expression of the model. Hence its inability to describe the phenomenon of temperature-induced softening. The equation that describes this model is given as follows \cite{Johnson-1985}:

>>>>

For several years, many researchers have developed methods to predict the thermomechanical behavior of materials under hot working conditions using constitutive models. Thus, various forms of constitutive equations have been proposed to describe the flow of materials, among which, phenomenological, semi-empirical, physical models or models based on Artificial Neural Networks (ANN) \cite{Lin-2011, Shin-2010, Rusinek-2010, Pantale-2021}. Among the large number of models available in the literature, the Johnson-Cook (JC) \cite{Johnson-1983} and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in finite element codes. The Johnson-Cook model is the most widely used because it is simple to identify and use and has few parameters to determine \cite{Khan-2004, NematNasser-2003}. However, this model, in its original state, has some shortcomings related to nonlinear coupling phenomena not taken into account in the material behavior. We refer here to strain hardening, strain rate hardening and thermal effects that are taken into account in a non-coupled manner in the JC model as analyzed by Jia \eal \cite{Jia-2021}. To circumvent these shortcomings, several modified forms of the Johnson-Cook model have been developed in the past \cite{Rule-1998, Vural-2003, Lin-2010, Lin-2012, Li-2013, Zhou-2019, Zhang-2015}. Due to its more physics-based formulation, the ZA model is often preferred to the JC model because it allows the coupling of strain rate and temperature effects \cite{Johnson-1988, Voyiadjis-2005, Dey-2007}. However, this model has other drawbacks related to the limit value of the test temperature. Indeed, this model applies only to low strain rates and for temperatures limited to about 60~\% of $T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005, Lee-2005, Chen-2007, Lee-2006}. Moreover, this model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009}. In order to reduce these shortcomings (and to apply this model to a wider range of temperatures) of the ZA model, modified forms of Zerilli-Armstrong (MZA) have been proposed by several authors in recent years \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}.

@@

The JC model as mentioned above, is one of the most widely used analytical models as it can be applied to several materials under different conditions of strain, strain rate and temperature. However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate and temperature. Indeed, it is formulated by describing the effect of each physical parameter (strain, strain rate and temperature) separately as a factor in the mathematical expression of the model. Hence its inability to describe the phenomenon of temperature-induced softening. The equation that describes this model is given as follows \cite{Johnson-1983}:
